Conversion of FFCS ICE fleet to EV: a data-driven approach

### 2020-11-16 Chapter10/10_5-results.tex
chapt
chap_9_parsed

Given the multiple system design parameters, here we proceed by steps. First we analyse the impact on performance in order to select good design options. We then project the results through the cost figures to gauge the economic implications of these choices.

We consider as starting parameters the ones referring to the current FFCS running in Turin based on ICE cars, i.e., a fleet size $|F|=400$ and demand scaling factor $\lambda=1$. We explore the charging infrastructure design options, namely its size $n_p$ and extensiveness $z_p$. We fix $\alpha=0.25$ corresponding to the minimum energy needed to perform the longest trip in Turin~\cite{7_cocca2019free}.
We also check the impact of increasing the demand up to $\lambda=5$. Correspondingly, we increase the fleet size $|F(\lambda)|=400\cdot \lambda$ by the same factor. Each simulation considers three months of virtual time, corresponding to more than 200\,000 rental requests for $\lambda=1$.

@@

Focus first on the impact of the number of poles per vehicles $n_p/|F|$ on the unsatisfied demand - reported in Figure~\ref{fig:10_5_unsatisfied_load1_zp5}. Consider $\lambda=1$ first. Here $z_p=0.05$ (14 charging zones). We observe two working regions: on the right - the charging infrastructure has enough capacity to supply the energy to support all customers' trips - resulting in a constant unsatisfied demand. On the left, system charging capacity goes below a minimum threshold (highlighted by the red area). Here the charging infrastructure cannot supply enough energy and unfeasible trips grow linearly with the lack of energy.
Consider now a demand factor that doubles ($\lambda=2$, and $|F|=2\cdot 400$). The energy supply must grow by a factor of 2 to supply twice the number of trips. As such the minimum threshold in terms of number of poles per vehicles remains the same. The same holds for higher $\lambda$.
Interestingly, the number of poles to supply the energy to cope with the mobility demand is quite small: a pole every 20 cars results enough.

There is still a 5-7\% of unsatisfied demand which results from the mismatch between zones with available cars, and zones with demand. We now check the impact of $z_p$ on this.
Figure~\ref{fig:10_5_unsatisfied_zp} fixes $n_p/|F|=0.06$, and shows the impact of concentrating or spreading them on few or more zones. On the leftmost case, we have the ``charging hub'' scenario, meaning that all poles are located in a single zone where all cars must be brought for charging. This solution creates a surplus of cars in the zone where the hub is, and a lack of cars in other zones. Unsatisfied demand then grows, calling for relocation policies.
Increasing $z_p$ has the benefit of spreading cars in the city\footnote{For $\lambda=1$ we can equip $n_p=24$ zone maximum ($z_p=0.09$), after which results do not change. Differences are due to simulation randomness.}. Having opted to place poles in $top\_{park}$ zones, cars get naturally located there, facilitating customers that look for a car in those high-demand zones. This reduces the percentage of unsatisfied demand significantly, questioning the need of costly relocation policies. Performance-wise, the higher the fraction of zones with poles, the better.

@@

Focus now on the time the system has to spend to bring cars to the closest charging pole, reported in Figure~\ref{fig:10_5_zp_relocost} for $z_p=0.20$. 
Notice that if the system cannot supply enough energy to satisfy the demand ($n_p/|F|<0.055$ in this case), the charging handling cost decreases. Likely not a good design choice being this due to loss of satisfied demand.
Consider the region $n_p/|F|\geq 0.055$, where the system has enough charging capacity. If there are just enough poles, most of them results busy, and the workers need to drive cars to far away free poles. This results in an increase of handling time up to 1600\,$h$ for $\lambda=5$. By increasing $n_p/|F|$, we increase the probability of finding a nearby free pole, shortening handling time down to 1000\,$h$ per  month for $\lambda=5$.
As expected, the higher $\lambda$, the higher the time to handle charging events -- with an almost perfect linear increase.

This highlights a trade-off between infrastructure costs and management costs. To better gauge this, Figure~\ref{fig:10_5_zp_gain} compares a more concentrated system with $z_p=0.05$ with a more distributed system with $z_p=0.20$. We plot the "additional satisfied demand" (black curve) and the saving in charging handling time (red curve) for increasing demand factor $\lambda$ and fleet size $|F|$ (fixing $n_p/|F|$ = 0.06). In all cases, $z_p=0.20$ results in higher satisfied demand and lower cost than $z_p=0.05$, with benefits that increase with increasing demand. In a nutshell, distributing the same number of poles among more zones improves system performance and reduces charging handling time. Clearly this needs to be weighted by the additional cost of installing a more distributed charging infrastructure.

\subsection{Impact of fleet size}
We now explore the impact of the number of cars when the demand increases. For this, we scale $\lambda$, but keep the fleet size constant to $|F|=400$. For simplicity, we consider a  charging infrastructure capacity that can cope with the highest demand, i.e., $n_p=120$. We consider two cases, $z_p=0.05$ and $z_p=0.20$. We plot results in Figure~\ref{fig:10_5_unsatisfied_zp_fixed_request}.
Interestingly, the same number of vehicles can sustain a sizeable increase in $\lambda$ without a significant impact the unsatisfied demand. 
For instance, $|F|=400$ vehicles can cope with a factor $\lambda=3$ increase in the demand, just losing 2.5\% of customer requests. This would result in a significant saving in the cost of vehicles. Given there are no differences in concentrating or spreading the charging poles in few or more zones, we fix $z_p=0.20$ from now on.

@@

To observe how the unsatisfied demand would be impaired by further reducing the number of cars and/or the number of poles, we present contour maps in Figures~\ref{fig:10_5_contour_unsatisfied_rate-1} and Figure~\ref{fig:10_5_contour_unsatisfied_rate-5}, for $\lambda=1$ and $\lambda=5$, respectively. 
Interestingly, the two design parameters seem to affect unsatisfied demand in almost independent manner. On the one hand, reducing the number of cars has limited impact until we reach very small values. For instance, halving the fleet size down to $|F|=200$ would increase the unsatisfied demand by 6-8\% only.
On the other hand, increasing $n_p$ brings no benefit - provided there are enough poles (cfr. Figure~\ref{fig:10_5_unsatisfied_load1_zp5}).

@@

%It is quite a result because we can face a quintupled demand doubling our fleet. Indeed, there seems to be a value for the number of poles that guarantees that specific fraction of unsatisfied users. After reaching this number of poles if we keep on increasing one of the two parameters we can not appreciate any differences in terms of this performance metric.

@@

To have a clear and complete picture, we now project the performance indexes into economic figures. Here we compare the monthly profit an EVs FFCS provider would reach for different combinations of the number of vehicles and the number of poles, i.e., its investment in the fleet and charging infrastructure. All costs included in Table~\ref{tab:summary} are considered.

Figure~\ref{fig:10_5_profits_rate-1} shows the results for $\lambda=1$. Green shades reflect positive profit, while yellow and red shades highlight loss-making configurations. Interestingly, the zones with the highest profits tend to be in the leftmost part of the figure, i.e., for small number of cars. While this causes a higher unsatisfied demand - see Figure~\ref{fig:10_5_contour_unsatisfied_rate-1} - it looks the only way to reduce the cost of the fleet so to have a profitable system. The impact of the charging infrastructure is quite negligible unless when $n_p$ becomes too small (i.e., when not enough charging capacity is present). This is due to the low cost of buying and installing a charging pole when amortized on $p_{life}=10$ years. Recall that we have seen that the charging infrastructure design calls for a charging pole every 20 vehicles. As such, the overall economic impact of the charging infrastructure results quite negligible compared to the fleet size costs.

The picture improves drastically when $\lambda=5$, shown in Figure~\ref{fig:10_5_profits_rate-5}. Here, we explore scenarios with a 5-fold increase in both the number of poles ($n_p\in[50,300])$, and in the number of vehicles ($|F|\in[400,2000]$) with respect to the $\lambda=1$ scenario. Here, all configurations result in positive profit. Even more interestingly, by reducing the number of cars we observe a marginal decrease in the profit, with the best scenarios being in $|F|\in[1400, 2000]$. This is due to large multiplexing effect we already observed in Figure~\ref{fig:10_5_unsatisfied_zp_fixed_request}. Even when reducing the number of cars to 800, we observe sizeable profits.

Considering the number of poles, as expected, when $n_p<120$ (the minimum threshold for constant unsatisfied demand when $|F|=2000$, showed in Figure~\ref{fig:10_5_unsatisfied_load1_zp5}) the insufficient system charging capacity impairs cars availability, increasing the unsatisfied demand. 
As seen already, increasing $n_p$ above the minimum threshold brings little benefit, but it also has little impact on the profits (due to the relatively low cost of pole installation).

In summary, we can conclude that the FFCS provider needs to carefully evaluate the minimum number of poles when designing and implementing the charging infrastructure. The limited cost of pole installation, and the long amortization time make overprovisioning the charging infrastructure a viable option to make the system robust to demand increase.
Considering the fleet size, when the demand is low, the high cost of vehicles suggests limiting the number of vehicles. When instead the demand grows, an economy of scale gain is possible, making the system even profitable with large fleet size.

>>>>

Given the multiple system design parameters, here I proceed by steps. First I analyse the impact on performance in order to select good design options. I then project the results through the cost figures to gauge the economic implications of these choices.

I consider as starting parameters the ones referring to the current FFCS running in Turin based on ICE cars, i.e., a fleet size $|F|=400$ and demand scaling factor $\lambda=1$. I explore the charging infrastructure design options, namely its size $n_p$ and extensiveness $z_p$. I fix $\alpha=0.25$ corresponding to the minimum energy needed to perform the longest trip in Turin~\cite{7_cocca2019free}.
I also check the impact of increasing the demand up to $\lambda=5$. Correspondingly, I increase the fleet size $|F(\lambda)|=400\cdot \lambda$ by the same factor. Each simulation considers three months of virtual time, corresponding to more than 200\,000 rental requests for $\lambda=1$.

@@

Focus first on the impact of the number of poles per vehicles $n_p/|F|$ on the unsatisfied demand - reported in figure~\ref{fig:10_5_unsatisfied_load1_zp5}. Consider $\lambda=1$ first. Here $z_p=0.05$ (14 charging zones). I observe two working regions: on the right - the charging infrastructure has enough capacity to supply the energy to support all customers' trips - resulting in a constant unsatisfied demand. On the left, system charging capacity goes below a minimum threshold (highlighted by the red area). Here the charging infrastructure cannot supply enough energy and unfeasible trips grow linearly with the lack of energy.
Consider now a demand factor that doubles ($\lambda=2$, and $|F|=2\cdot 400$). The energy supply must grow by a factor of 2 to supply twice the number of trips. As such the minimum threshold in terms of number of poles per vehicles remains the same. The same holds for higher $\lambda$.
Interestingly, the number of poles to supply the energy to cope with the mobility demand is quite small: a pole every 20 cars results enough.

There is still a 5-7\% of unsatisfied demand which results from the mismatch between zones with available cars, and zones with demand. I now check the impact of $z_p$ on this.
figure~\ref{fig:10_5_unsatisfied_zp} fixes $n_p/|F|=0.06$, and shows the impact of concentrating or spreading them on few or more zones. On the leftmost case, I have the ``charging hub'' scenario, meaning that all poles are located in a single zone where all cars must be brought for charging. This solution creates a surplus of cars in the zone where the hub is, and a lack of cars in other zones. Unsatisfied demand then grows, calling for relocation policies.
Increasing $z_p$ has the benefit of spreading cars in the city\footnote{For $\lambda=1$ I can equip $n_p=24$ zone maximum ($z_p=0.09$), after which results do not change. Differences are due to simulation randomness.}. Having opted to place poles in $top\_{park}$ zones, cars get naturally located there, facilitating customers that look for a car in those high-demand zones. This reduces the percentage of unsatisfied demand significantly, questioning the need of costly relocation policies. Performance-wise, the higher the fraction of zones with poles, the better.

@@

Focus now on the time the system has to spend to bring cars to the closest charging pole, reported in figure~\ref{fig:10_5_zp_relocost} for $z_p=0.20$. 
Notice that if the system cannot supply enough energy to satisfy the demand ($n_p/|F|<0.055$ in this case), the charging handling cost decreases. Likely not a good design choice being this due to loss of satisfied demand.
Consider the region $n_p/|F|\geq 0.055$, where the system has enough charging capacity. If there are just enough poles, most of them results busy, and the workers need to drive cars to far away free poles. This results in an increase of handling time up to 1600\,$h$ for $\lambda=5$. By increasing $n_p/|F|$, I increase the probability of finding a nearby free pole, shortening handling time down to 1000\,$h$ per  month for $\lambda=5$.
As expected, the higher $\lambda$, the higher the time to handle charging events -- with an almost perfect linear increase.

This highlights a trade-off between infrastructure costs and management costs. To better gauge this, figure~\ref{fig:10_5_zp_gain} compares a more concentrated system with $z_p=0.05$ with a more distributed system with $z_p=0.20$. I plot the "additional satisfied demand" (black curve) and the saving in charging handling time (red curve) for increasing demand factor $\lambda$ and fleet size $|F|$ (fixing $n_p/|F|$ = 0.06). In all cases, $z_p=0.20$ results in higher satisfied demand and lower cost than $z_p=0.05$, with benefits that increase with increasing demand. In a nutshell, distributing the same number of poles among more zones improves system performance and reduces charging handling time. Clearly this needs to be weighted by the additional cost of installing a more distributed charging infrastructure.

\subsection{Impact of fleet size}
I now explore the impact of the number of cars when the demand increases. For this, I scale $\lambda$, but keep the fleet size constant to $|F|=400$. For simplicity, I consider a  charging infrastructure capacity that can cope with the highest demand, i.e., $n_p=120$. I consider two cases, $z_p=0.05$ and $z_p=0.20$. I plot results in figure~\ref{fig:10_5_unsatisfied_zp_fixed_request}.
Interestingly, the same number of vehicles can sustain a sizeable increase in $\lambda$ without a significant impact the unsatisfied demand. 
For instance, $|F|=400$ vehicles can cope with a factor $\lambda=3$ increase in the demand, just losing 2.5\% of customer requests. This would result in a significant saving in the cost of vehicles. Given there are no differences in concentrating or spreading the charging poles in few or more zones, I fix $z_p=0.20$ from now on.

@@

To observe how the unsatisfied demand would be impaired by further reducing the number of cars and/or the number of poles, I present contour maps in Figures~\ref{fig:10_5_contour_unsatisfied_rate-1} and figure~\ref{fig:10_5_contour_unsatisfied_rate-5}, for $\lambda=1$ and $\lambda=5$, respectively. 
Interestingly, the two design parameters seem to affect unsatisfied demand in almost independent manner. On the one hand, reducing the number of cars has limited impact until I reach very small values. For instance, halving the fleet size down to $|F|=200$ would increase the unsatisfied demand by 6-8\% only.
On the other hand, increasing $n_p$ brings no benefit - provided there are enough poles (cfr. figure~\ref{fig:10_5_unsatisfied_load1_zp5}).

@@

%It is quite a result because I can face a quintupled demand doubling our fleet. Indeed, there seems to be a value for the number of poles that guarantees that specific fraction of unsatisfied users. After reaching this number of poles if I keep on increasing one of the two parameters I can not appreciate any differences in terms of this performance metric.

@@

To have a clear and complete picture, I now project the performance indexes into economic figures. Here I compare the monthly profit an EVs FFCS provider would reach for different combinations of the number of vehicles and the number of poles, i.e., its investment in the fleet and charging infrastructure. All costs included in Table~\ref{tab:summary} are considered.

figure~\ref{fig:10_5_profits_rate-1} shows the results for $\lambda=1$. Green shades reflect positive profit, while yellow and red shades highlight loss-making configurations. Interestingly, the zones with the highest profits tend to be in the leftmost part of the figure, i.e., for small number of cars. While this causes a higher unsatisfied demand - see figure~\ref{fig:10_5_contour_unsatisfied_rate-1} - it looks the only way to reduce the cost of the fleet so to have a profitable system. The impact of the charging infrastructure is quite negligible unless when $n_p$ becomes too small (i.e., when not enough charging capacity is present). This is due to the low cost of buying and installing a charging pole when amortized on $p_{life}=10$ years. Recall that I have seen that the charging infrastructure design calls for a charging pole every 20 vehicles. As such, the overall economic impact of the charging infrastructure results quite negligible compared to the fleet size costs.

The picture improves drastically when $\lambda=5$, shown in figure~\ref{fig:10_5_profits_rate-5}. Here, I explore scenarios with a 5-fold increase in both the number of poles ($n_p\in[50,300])$, and in the number of vehicles ($|F|\in[400,2000]$) with respect to the $\lambda=1$ scenario. Here, all configurations result in positive profit. Even more interestingly, by reducing the number of cars I observe a marginal decrease in the profit, with the best scenarios being in $|F|\in[1400, 2000]$. This is due to large multiplexing effect I already observed in figure~\ref{fig:10_5_unsatisfied_zp_fixed_request}. Even when reducing the number of cars to 800, I observe sizeable profits.

Considering the number of poles, as expected, when $n_p<120$ (the minimum threshold for constant unsatisfied demand when $|F|=2000$, showed in figure~\ref{fig:10_5_unsatisfied_load1_zp5}) the insufficient system charging capacity impairs cars availability, increasing the unsatisfied demand. 
As seen already, increasing $n_p$ above the minimum threshold brings little benefit, but it also has little impact on the profits (due to the relatively low cost of pole installation).

In summary, I can conclude that the FFCS provider needs to carefully evaluate the minimum number of poles when designing and implementing the charging infrastructure. The limited cost of pole installation, and the long amortization time make overprovisioning the charging infrastructure a viable option to make the system robust to demand increase.
Considering the fleet size, when the demand is low, the high cost of vehicles suggests limiting the number of vehicles. When instead the demand grows, an economy of scale gain is possible, making the system even profitable with large fleet size.

### 2020-11-16 Chapter10/10_6-conclusions.tex
chap_9_parsed

In this paper we presented a simulation study of free floating car sharing systems. Armed with a realistic demand, we studied the performance implications of moving from ICE FFCS to a EV based solution.

Our study offers several take-away messages: first, the charging infrastructure must be able to provide enough energy to cope with the mobility demand. Interestingly, it results to be quite limited, with just 20 poles able to sustain a system of 400 vehicles.
Second, distributing the charging poles in zones where cars get frequently parked and rented is instrumental to maximize the demand the system can satisfy, while also limiting the time workers have to spend to bring cars for charging.
Third, the system exhibits useful economy of scale, so that the fleet size shall increase sublinearly with respect to the mobility demand intensity.

@@

As future direction, we are studying different cities as new use cases, looking at opportunities of involving users in the charging process in order to decrease management costs.

>>>>

In this chapter I presented a simulation study of free floating car sharing systems. Armed with a realistic demand, I studied the performance implications of moving from ICE FFCS to a EV based solution.

This study offers several take-away messages: first, the charging infrastructure must be able to provide enough energy to cope with the mobility demand. Interestingly, it results to be quite limited, with just 20 poles able to sustain a system of 400 vehicles.
Second, distributing the charging poles in zones where cars get frequently parked and rented is instrumental to maximize the demand the system can satisfy, while also limiting the time workers have to spend to bring cars for charging.
Third, the system exhibits useful economy of scale, so that the fleet size shall increase sublinearly with respect to the mobility demand intensity.

@@

As future direction, I are studying different cities as new use cases, looking at opportunities of involving users in the charging process in order to decrease management costs.

### 2020-11-16 Chapter8/8_4_temporal_analyses.tex
chap_9_parsed

Table~\ref{tab:8_4_results-stationary-models} shows the average mean absolute percentage error (MAPE), the standard deviation of the APE, and the RMSE for each of the prediction models.
%\ana{it is missing to cite the other measures.} 
The models that rely only on the time series (ARIMA and SARIMA) are able to capture some patterns in the data, as their performance is considerably better than the baseline. However, the multivariate models perform better, with Random Forest Regression reaching the best performances. In figure~\ref{fig:random-forests-stationary} we show the comparison between the actual values and the prediction in one month of the validation set using the Random Forest Regression model (orange dashed line). Overall the model is able to predict quite well the daily and weekly periodicity of rentals, but in general slightly underestimates the actual number of rentals. This could be due to the fact the training period refers to the first six months of the year, during which the average number of rentals is lower than during the validation period in fall.

>>>>

Table~\ref{tab:8_4_results-stationary-models} shows the average mean absolute percentage error (MAPE), the standard deviation of the APE, and the RMSE for each of the prediction models.
%\ana{it is missing to cite the other measures.} 
The models that rely only on the time series (ARIMA and SARIMA) are able to capture some patterns in the data, as their performance is considerably better than the baseline. However, the multivariate models perform better, with Random Forest Regression reaching the best performances. In figure~\ref{fig:8_4_random-forests-stationary} we show the comparison between the actual values and the prediction in one month of the validation set using the Random Forest Regression model (orange dashed line). Overall the model is able to predict quite well the daily and weekly periodicity of rentals, but in general slightly underestimates the actual number of rentals. This could be due to the fact the training period refers to the first six months of the year, during which the average number of rentals is lower than during the validation period in fall.

### 2020-11-16 Chapter8/8_5_spatyal_analyses.tex
chap_9_parsed

To evaluate the impact of the features on the model performance, I train once again the RFR with an increasing number of features, chosen according to the given rank. I fix the number of trees according to the best average MAPE obtained in Figures~\ref{fig:8_5_rfr_start_MAPE} and \ref{fig:8_5_rfr_final_MAPE}: 40 trees for the starting and 20 for the ending rentals prediction. Figure~\ref{fig:reg_err_perc_LC} shows the results. It reports the MAPE versus the number of features in the model.
Notice the U-shaped curve of the average MAPE (dashed black line). Intuitively, too few features worsen the regression performance due to lack of information. Too many features also reduce the performance since the training is more complicated and the model gets confused.

I further evaluate the RFR model by selecting the best number of features (the one that minimizes the average MAPE), which results to selecting the top 7 features in Table~\ref{tab:results-stationary-models}. With this subset, the average MAPE is 41\% and RMSE equals to 1104.501 for starting rentals, while for arrivals
MAPE is 39\% and  RSME is equal to 1010.453.%\ana{Michele, please check the values.}.
As expected, using only the top most important features improves significantly the performance.

>>>>

To evaluate the impact of the features on the model performance, I train once again the RFR with an increasing number of features, chosen according to the given rank. I fix the number of trees according to the best average MAPE obtained in Figures~\ref{fig:8_5_rfr_start_MAPE} and \ref{fig:8_5_rfr_final_MAPE}: 40 trees for the starting and 20 for the ending rentals prediction. Figure~\ref{fig:8_5_reg_err_perc_LC} shows the results. It reports the MAPE versus the number of features in the model.
Notice the U-shaped curve of the average MAPE (dashed black line). Intuitively, too few features worsen the regression performance due to lack of information. Too many features also reduce the performance since the training is more complicated and the model gets confused.

I further evaluate the RFR model by selecting the best number of features (the one that minimizes the average MAPE), which results to selecting the top 7 features in Table~\ref{tab:8_5_featuresranking}. With this subset, the average MAPE is 41\% and RMSE equals to 1104.501 for starting rentals, while for arrivals
MAPE is 39\% and  RSME is equal to 1010.453. 
As expected, using only the top most important features improves significantly the performance.

### 2020-11-16 thesis.tex
added_chap_10
chapt
chap_9_parsed

%%%% Use the following package if and only if you want to produce
%%%% an archivable document according to standard PDF/A-1b
%%%% No need to load package imakeidx, because it has already been
%%%% loaded by the specific module toptesi-scudo.
\usepackage[a-1b]{pdfx}
\usepackage[linesnumbered,ruled,norelsize]{algorithm2e}
\newtheorem{definition}{Definition}
%%%%%% Read the English documentation of TOPtesi in order to check
%%%%%% the special attention needed to produce ISO compliant
%%%%%% archivable files
%%%%

@@

\usepackage{kantlipsum,mwe} % to produce dummy text and dummy figures

@@

%%%% The \includeonly argument should preferably be written with
%%%% one file name per line, so that by commenting or uncommenting
%%%% some lines a selective compilation may be executed.
\includeonly{%
Chapter1/1_introduction,%
Chapter2/2_datacollection,%
Chapter3/3_datacharact,%
Chapter4/4_cs_comparison,%
Chapter5/5_simulator,
Chapter6/6_4cities,
Chapter7/7_cs_optimization,
Chapter8/8_prediction,
Chapter9/9_relocation,
Chapter10/10_scalability,
Chapter11/11_conclusion
%Appendix1/appendix1,
%Appendix2/appendix2,%
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\tool}{\textit{UMAP}\xspace}
\newcommand{\MGM}[1]{#1}
\newcommand{\removelatexerror}{\let\@latex@error\@gobble}
\newcommand{\reviewed}[1]{{\color{black}{#1}}}
\newcommand{\mc}[1]{{\color{purple}{[mike: #1]}}}
\usepackage[thinlines]{easytable}

@@

\title{Conversion of FFCS ICE fleet to EV}

@@

\subtitle{a data-driven approach}

@@

\include{Chapter1/1_introduction}
\include{Chapter2/2_datacollection}
\include{Chapter3/3_datacharact}
\include{Chapter4/4_cs_comparison}
\include{Chapter5/5_simulator}
\include{Chapter6/6_4cities}
\include{Chapter7/7_cs_optimization}
\include{Chapter8/8_prediction}
\include{Chapter9/9_relocation}
\include{Chapter10/10_scalability}
\include{Chapter11/11_conclusion}
%% Numbered appendices remain in the main matter...
%\appendix
%\include{Appendix1/appendix1}
%\include{Appendix2/appendix2}

>>>>

%%%% Use the following package if and only if you want to produce
%%%% an archivable document according to standard PDF/A-1b
%%%% No need to load package imakeidx, because it has already been
%%%% loaded by the specific module toptesi-scudo.
\usepackage[a-1b]{pdfx}
\usepackage[linesnumbered,ruled,norelsize]{algorithm2e}

\newtheorem{definition}{Definition}
%%%%%% Read the English documentation of TOPtesi in order to check
%%%%%% the special attention needed to produce ISO compliant
%%%%%% archivable files
%%%%

@@

\usepackage{kantlipsum,mwe} % to produce dummy text and dummy figures
\usepackage{booktabs}

@@

%%%% The \includeonly argument should preferably be written with
%%%% one file name per line, so that by commenting or uncommenting
%%%% some lines a selective compilation may be executed.
\includeonly{%
Chapter1/1_introduction,%
Chapter2/2_datacollection,%
Chapter3/3_datacharact,%
Chapter4/4_cs_comparison,%
Chapter5/5_simulator,
Chapter6/6_4cities,
Chapter7/7_cs_optimization,
Chapter8/8_prediction,
%Chapter9/9_relocation,
Chapter10/10_scalability,
Chapter11/11_conclusion
%Appendix1/appendix1,
%Appendix2/appendix2,%
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\tool}{\textit{UMAP}\xspace}
\newcommand{\MGM}[1]{#1}
\newcommand{\removelatexerror}{\let\@latex@error\@gobble}
\newcommand{\reviewed}[1]{{\color{black}{#1}}}
\newcommand{\mc}[1]{{\color{purple}{[mike: #1]}}}
\usepackage[thinlines]{easytable}

@@

\title{Electric Revolution and\\Free Floating Car Sharing}

@@

\subtitle{A Data Driven Methodology for System Design}

@@

\include{Chapter1/1_introduction}
\include{Chapter2/2_datacollection}
\include{Chapter3/3_datacharact}
\include{Chapter4/4_cs_comparison}
\include{Chapter5/5_simulator}
\include{Chapter6/6_4cities}
\include{Chapter7/7_cs_optimization}
\include{Chapter8/8_prediction}
%\include{Chapter9/9_relocation}
\include{Chapter10/10_scalability}
\include{Chapter11/11_conclusion}
%% Numbered appendices remain in the main matter...
%\appendix
%\include{Appendix1/appendix1}
%\include{Appendix2/appendix2}
